A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-01-21 sections/Metatheory.tex
Metatheory: lemmas and theorems.

\subsection{Soundness}
\subsection{Completeness}
\subsection{Decidability}

>>>>

\begin{lemma}[Insert]
If $\Gm_L\vdash \tau$ and $\Gm_L, [\tau/\al]\Gm_R \sto \Om$
, then $\Gm_L, \al, \Gm_R \sto \Om$.
\end{lemma}
\begin{lemma}[Extract]
If $\Gm_L, \al, \Gm_R \sto \Om$
, then $\exists \tau$ s.t. $\Gm\vdash\tau$ and $\Gm_L, [\tau/\al]\Gm_R \sto \Om$.
\end{lemma}

\subsection{Soundness}

\begin{theorem}[Soundness]
If \emph{wf }$\Gm$ and $\Gm \redto \cdot$, then $\exists \Om$ s.t. $\Gm\sto\Om$ and $\Om\redto\cdot$.
\end{theorem}

\subsection{Completeness}

\begin{theorem}[Completeness]
If \emph{wf }$\Gm$ and $\exists \Om$ s.t. $\Gm\sto\Om$ and $\Om\redto\cdot$, then $\Gm \redto \cdot$.
\end{theorem}

\begin{lemma}[Prune Transfer for Instantiation]
If $(\Gm \vdash \al \le A \to B) \sto (\Om \vdash C \le A_1 \to B_1)$ and $\Om \vdash_d C \le A_1 \to B_1$,
then $\al\notin FV(A) \cup FV(B)$.
\end{lemma}

\subsection{Decidability}
\begin{theorem}[Decidability]
For all well-formed $\Gm$, it is decidable whether $\Gm\redto\cdot$ or not.
\end{theorem}

lexicographic group of induction measurements
$\langle |\Gm|_e, |\Gm|_\Leftrightarrow, |\Gm|_\forall, |\Gm|_{\al}, |\Gm|_\to + |\Gm| \rangle$

\begin{definition}[Worklist Measures]
\[|\Gm|_e = \sum_{e\Lto A\in\Gm}|e|_e + \sum_{e\To_a \jg\in\Gm}|e|_e + \sum_{\appInfAlg{A}{e}\in\Gm}|e|_e\]
\[|\Gm|_\Leftrightarrow = \#_{e\Lto A\in\Gm}
    + 2\cdot\#_{e\To_a \jg\in\Gm} + 3\cdot\#_{\appInfAlg{A}{e}\in\Gm}\]
\[|\Gm|_\forall = \sum_{e\Lto A\in\Gm}|A|_\forall + \sum_{\appInfAlg{A}{e}\in\Gm}|A|_\forall +
    \sum_{A\le B\in\Gm} |A|_\forall + |B|_\forall\]
\[|\Gm|_\to = \sum_{e\Lto A\in\Gm}|A|_\to + \sum_{\appInfAlg{A}{e}\in\Gm}|A|_\to +
    \sum_{A\le B\in\Gm} |A|_\to + |B|_\to\]
\[|\Gm|_{\al} = \#_{\al\in\Gm}\]
\end{definition}
